\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-23 manuscript/main.tex
new file:   figures/distribution_of_ten_cities.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   plotting/plotting_distribution_of_offline_stores_in_different_cities.R

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation. By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of these stores on housing transactions. Incorporating this optimal influence radius, the study further investigates the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the Covid-19. However, this effect is attenuated during the Covid-19 period due to remote work and other restrictive policies implemented by the Chinese government. Additionally, the paper explores the impact of Lianjia's Agent Cooperation Network (ACN) strategy on its platform consolidation effect, concluding that this strategy enhances Lianjia's revenue generation and facilitates transactions. This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting future trajectories in the evolving real estate brokerage market.
  \end{abstract}

  \textbf{Keyword}: Marketing Strategy, Housing Markets, Digital Platforms

@@

In the real estate market, transaction cost is a critical factor for both buyers and sellers. Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties. Real estate brokers not only help in reducing transaction costs but also provide essential market information, negotiation support, and legal assistance, thereby ensuring smoother and more efficient transactions. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}. Their expertise and local market knowledge have become indispensable in navigating the complex real estate landscape.

The Chinese real estate brokerage market has long been characterized by intense competition among offline stores, with multiple brokerages establishing a presence within the same community to vie for clients. However, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.

Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats. This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

Through the success of the platform consolidation, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence. More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources. For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%. This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape. The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market. [NEED TO ADD A FIGURE OR TABLE]

@@

@@

@@

\section{Appendix Tables and Figures}
% \input{tab_tex/other-regressions.tex}

>>>>

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation. By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores on housing transactions. Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and online platform consolidation on transaction properties. This analysis leverages the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the COVID-19 pandemic. However, this effect diminishes during the pandemic due to remote work and restrictive policies implemented by the Chinese government. The study also examines the online platform consolidation effect by analyzing the period in 2018 when Lianjia revised and improved its Agent Cooperation Network (ACN).

    \textbf{The results indicate that this strategy significantly boosts revenues and also suggest that the offline store's effect is majorly focused on people's transaction behaviors but the online platform's effect can be more insightful to provide a more efficient transaction process. } % this need to be revised.

    This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
  \end{abstract}

  \textbf{Keyword}: Marketing Strategy, Digital Platforms, Platform Consolidation, Real Estate Brokerage

@@

Understanding housing markets is crucial due to their significant impact on household finance, as housing is typically the largest component of a household's portfolio. The illiquidity of housing creates a strong link between housing and labor markets, and transaction costs are critical for buyers and sellers in the real estate market. Real estate brokers play a vital role in reducing these costs, providing essential market information, negotiation support, and legal assistance to ensure smoother and more efficient transactions. With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}. Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

The Chinese real estate brokerage market has long been characterized by intense competition among offline stores, with multiple brokerages establishing a presence within the same community to vie for clients. However, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China. Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats. This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

Through the success of the platform consolidation, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence. More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources. According to the IPO prospectus by Beke, the market share of Lianjia is around 20.8\% in year 2020 in China's second hand housing market and the number of stores share in the whole China is less than 5\% according to the AutoNavi map and moreover, in large cities like Chengdu, Beijing and Shanghai, the second hand housing share of Lianjia is even larger to

This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape. The Figure \ref{fig:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market. [NEED TO ADD A FIGURE OR TABLE]

@@

% Accodring to 招股书，链家在2021的成交是cross store占比76\%

@@

The Chinese real estate market witnessed a significnat drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.

@@

\section{Appendix Tables and Figures}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_ten_cities.pdf}
  \caption{Distribution of Ten Cities's Brokerages Store Shares}
  \label{fig:distribution_store_shares}
  Note: the x-axis is city's name and the y-axis is the offline brokerage's stores share in the city. The data source is from AutoNavi Map.
\end{figure}

% \input{tab_tex/other-regressions.tex}
